### 2023-04-17 main.tex
thermalization

that is composed by a copy of $\mathcal{S}_{1}$ acting at site $x$ and with identities acting at all other sites of the chain. 

@@

 	\mathcal{S}_{2}:=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}^{x}\right)}%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
that is composed by a copy of $\mathcal{S}_{2}$ acting at site $x$ and with identities acting at all other sites of the chain. 

@@

H=\mathcal{S}^{-1}H^{''}\mathcal{S}

@@

	|\Psi\rangle=\mathcal{S}^{-1}|\Psi^{''}\rangle

@@

			\Psi^{'}(\bm{s})=\sum_{x=1}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}

@@

%Because of the exponent $(1-\delta_{s_{x},1})$, the element $\Psi^{''}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{s_{y}}\right)^{(1-c_{y})(1-\delta_{s_{y},1})}
	\end{split}
\end{equation} 
%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{s_{x}}$. 
Finally, considering all possible configurations $\bm{s}$, we obtain \eqref{ABS-vect}.
\begin{flushright}
    $\square$
\end{flushright}
\subsubsection{The steady state of $H$}\label{subsectionSSH}
The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
\begin{equation}\label{steadyStateH}
    |\Psi\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\Psi(\bm{s})|\bm{s}\rangle
\end{equation}
where for every $(s_{1},\ldots,s_{L})=\bm{s}$
\begin{equation}\label{steadyStateH-coeff}
    \begin{split}
        \Psi(\bm{s})&=\sum_{x=1}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
        \\&+
        \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right) 
        \sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}
\\&
\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
  \prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
 \\ &
 \beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
 \prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
    \end{split}
\end{equation}
\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $s_{x}\neq 1$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
\begin{equation}\label{LinkABS-corr}
\Psi(\bm{s})=\Psi^{'}(\bm{s})
\end{equation}
When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.

@@

	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})|}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}

@@

>>>>

that is composed by a copy of $\mathcal{S}_{1}$ (introduced in \eqref{S1Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 

@@

 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=2}^{N}\beta_{a}e_{a1}^{x}\right)}%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
that is composed by a copy of $\mathcal{S}_{2}$ (introduced in \eqref{S2Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 

@@

H=S^{-1}H^{''}S

@@

	|\Psi\rangle=S^{-1}|\Psi^{''}\rangle

@@

			\Psi^{'}(\bm{s})=\sum_{c_{1}=0}^{\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{y}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}

@@

%Because of the exponent $(1-\delta_{s_{x},1})$, the element $\Psi^{''}(\bm{s})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{s_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{s_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{s_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\mathbf{s})=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{x=1}^{L}c_{x})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\left(\beta_{s_{y}}\right)^{(1-c_{y})(1-\delta_{s_{y},1})}
	\end{split}
\end{equation} 
%Indeed, when $c_{i}=0$ this formula replaces the contribution in the square brackets with a $\beta_{s_{x}}$. 
Finally, considering all possible configurations $\bm{s}$, we obtain \eqref{ABS-vect}.
\begin{flushright}
    $\square$
\end{flushright}
\subsubsection{The steady state of $H$}\label{subsectionSSH}
The steady state $|\Psi\rangle$ of the Hamiltonian $H$ is given by 
\begin{equation}\label{steadyStateH}
    |\Psi\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\Psi(\bm{s})|\bm{s}\rangle
\end{equation}
where for every $(s_{1},\ldots,s_{L})=\bm{s}$
\begin{equation}\label{steadyStateH-coeff}
    \begin{split}
        \Psi(\bm{s})&=\sum_{c_{1}=0}^{1-\delta_{s_{1},1}}\ldots\sum_{c_{L}=0}^{1-\delta_{s_{L},1}}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(L+2)}\prod_{y=1}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}\beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
        \\&+
        \sum_{b=1}^{L}(-1)^{b}\sum_{q_{1}=1}^{L}\sum_{q_{2}=q_{1}+1}^{L}\ldots\sum_{q_{b}=q_{b-1}+1}^{L}\left(\prod_{r=1}^{b}\delta_{s_{q_{r}},1}\right) 
        \sum_{r=1}^{b}\sum_{d_{q_{r}}=2}^{N}
\\&
\sum_{x=1\,:\, x\neq q_{1},\ldots,q_{b}}^{L}\sum_{c_{x}=0}^{1-\delta_{s_{x},1}}\sum_{p=1}^{b}\sum_{c_{q_{p}}=0}^{1}\frac{\Gamma(2+L-\sum_{z=1}^{L}c_{z})}{\Gamma(2+L)}
  \prod_{y=1\,:\, y\neq q_{1},\ldots,q_{b}}^{L}\left(\lambda_{s_{y}}\left(2+L-y-\sum_{j=y}^{L}c_{j}\right)\right)^{c_{y}}
 \\ &
 \beta_{s_{y}}^{(1-c_{y})(1-\delta_{s_{y},1})}
 \prod_{t=1}^{b}\lambda_{d_{q_{t}}}\left(2+L-q_{t}-\sum_{j=q_{t}}^{L}c_{j}\right)^{c_{q_{t}}}\beta_{d_{q_{t}}}^{(1-c_{q_{t}})}
    \end{split}
\end{equation}
\textbf{Remark}: we observe that if no holes are present in \eqref{steadyStateH-coeff}, i.e. if $s_{x}\neq 1$ $\forall x\in \{1,\ldots,L\}$, then the second addend vanishes and
\begin{equation}\label{LinkABS-corr}
\Psi(\bm{s})=\Psi^{'}(\bm{s})
\end{equation}
When the configuration has holes, the presence of the second addend is motivated by the dependence of the "empty" in a fixed site from all others types in the same site.

@@

	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}

@@

\subsection{Instantaneous thermalization}
In this subsection we aim to extend to the multi-species stirring process the concept of \textit{thermalization limit} (see \cite{carinci2013duality}). The thermalized process gives rise, for any pair nearest neighbour sites of the chain, to a redistribution of the total number of particles. The thermalized model that we present in this paper is obtained from the boundary driven model with generator \eqref{Generator} performing an \textit{instantaneous thermalization limit}: for each bond $(x,x+1)$ the total number of particles $\bm{\epsilon}=n^{x}+n^{x+1}$ is redistributed according to the reversible measure, conditioned on the conservation of $\bm{\epsilon}$. 
\subsubsection{The thermalization measure}
As already mentioned, we will redistribute particles on a bond according to a probability measure that is the reversible one \eqref{reversibleMeasure}, conditioned on the conservation of the particles on that bond. We denote
	\nu_{TH}(\bm{r}|\bm{\epsilon}):&=\mathbb{P}\left(n^{x}=\bm{r}|\eta^{x}+n^{x+1}=\bm{\epsilon}\right)
	=\mathbb{P}\left((n_{1}^{x},\ldots,n_{N}^{x})=
	(r_{1},\ldots,r_{N})\;|\;(n_{1}^{x}+n_{1}^{x+1},\ldots,n_{N}^{x}+n_{N}^{x+1})=(\epsilon_{1},\ldots,\epsilon_{N})\right)
	\epsilon_{1}=2\nu-\sum_{a=2}^{N}\epsilon_{a}\qquad r_{1}=\nu-\sum_{a=2}^{N}r_{a}
We construct this measure. Using the conditional probability and the fact that the reversible measure \eqref{reversibleMeasure} is product over the sites of the chain of multinomial distributions we have
\nu_{TH}(\bm{r}|\bm{\epsilon})&=\frac{\mathbb{P}\left(\left\{n^{x}=\bm{r}\right\}\,\cap\,\left\{n^{x}+n^{x+1}=\bm{\epsilon}\right\}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\bm{\epsilon}\right)}=\frac{\mathbb{P}\left(n^{x}=\bm{r}\right)\,\mathbb{P}\left(n^{x+1}=\bm{\epsilon}-\bm{r}\right)}{\mathbb{P}\left(n^{x}+n^{x+1}=\bm{\epsilon}\right)}
Moreover, it holds that 
\text{Multinomial}(\nu,\rho_{1},\ldots,\rho_{N})+\text{Multinomial}(\nu,\rho_{1},\ldots,\rho_{N})=\text{Multinomial}(2\nu,\rho_{1},\ldots,\rho_{N})
Therefore 
	\nu_{TH}(\bm{r}|\bm{\epsilon})=\frac{\binom{\nu}{r_{1},\ldots,r_{N}}\binom{\nu}{(\epsilon_{1}-r_{1}),\ldots,(\epsilon_{N}-r_{N})}}{\binom{2\nu}{\epsilon_{1}\ldots,\epsilon_{N}}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}
where we denote the multinomial coefficient
	\binom{\nu}{n_{1},\ldots,n_{N}}=\frac{\nu!}{n_{1}!\cdots n_{N}!}
provided that $n_{1}+\ldots+n_{N}=\nu$ and $n_{1},\ldots,n_{N}\in \mathbb{N}_{0}$. 
\subsubsection{Thermalized multi-species stirring process}
The thermalized multi-species stirring process is defined on the configuration space $\Omega$ introduced in \eqref{stateSpace} and its generator reads
\begin{equation}\label{thermalizedGenerator}
	\mathcal{L}^{TH}=\mathcal{L}_{1}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\mathcal{L}_{L}^{TH}
\begin{equation}\label{bulkThermalized}
	\mathcal{L}_{x,x+1}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{n_{1}^{x}+n_{1}^{x+1}}\ldots\sum_{r_{N}=0}^{n_{N}^{x}+n_{N}^{x+1}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}
	\left\{f(n^{1},\ldots,n^{x-1},\bm{r},n^{x}+n^{x+1}-\bm{r},n^{x+2},\ldots,n^{L})-f(\bm{n})\right\}\nu_{TH}(\bm{r}|\bm{\epsilon})
while
\begin{equation}\label{boundaryThermalized}
		\mathcal{L}_{1}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\nu}
The right boundary generator is defined in a similar way. The $\alpha$'s are replaced by $\beta$'s and the action is only on site $L$. 
\subsubsection{The dual thermalized process}
The thermalized dual process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the enlarged configuration space $\widetilde{\Omega}$ introduced in \eqref{dualStateSpace}. Its generator reads
		\widetilde{\mathcal{L}}^{TH}=\widetilde{\mathcal{L}}_{1}^{TH}+\sum_{x=1}^{L-1}\mathcal{L}_{x,x+1}^{TH}+\widetilde{\mathcal{L}}_{L}^{TH}
where $\mathcal{L}^{TH}_{x,x+1}$ is \eqref{bulkThermalized} and $\widetilde{\mathcal{L}}_{1}^{TH}$ and $\widetilde{\mathcal{L}}_{L}^{TH}$ are absorbing with rate $1$, i.e. 
		\widetilde{\mathcal{L}}_{1}^{TH}f(\bm{\xi})=\left\{f(\xi^{0}+\xi^{1},0,\xi^{2},\ldots,\xi^{N})-f(\bm{\xi})\right\}
and similarly $\widetilde{\mathcal{L}}_{L}^{TH}$. 
The duality function is 
	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
The proof of the duality consists in proving 
	\left(\mathcal{L}_{x,x+1}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{x,x+1}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad x\in \{1,\ldots,L-1\}\label{bulkDualityTH}\\
	\left(\mathcal{L}_{y}^{TH}D(\cdot,\bm{n})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\qquad y\in\{1,L\}\label{boundaryDualityTH}
Equation \eqref{bulkDualityTH} follows from the proof of the edge duality for the multi-species stirring process. To prove \eqref{boundaryDualityTH} we directly apply the generators on the duality function. For the sake of notation, we introduce 
	d_{x}(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}
First, we act with $\mathcal{L}_{1}^{TH}$ on $D(\bm{n},\bm{\xi})$. This action gives
\begin{align}\label{ProvaBordoTH}
	\left(\mathcal{L}_{1}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.
	\\&\nonumber
	\left.\prod_{b=2}^{N}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\nu}
Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{-r_{a}+r_{a}-\xi_{a}^{1}+\xi_{a}^{1}}$ and using the Multinomial Theorem we have that the first addend in the curly brackets is
\begin{align}\label{pezzo1}
	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.\nonumber
	\\&\nonumber
	\left.\prod_{b=2}^{N}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}\right\}	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\nu}\\=&
	\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}
Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{r_{a}-r_{a}}$ and by the multinomial Theorem, we have that the second addend in the curly bracket is
\begin{equation}\label{pezzo2}
	&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\nu}\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{r_{a}-r_{a}}\\=&D(\bm{n},\bm{\xi})
Therefore, replacing \eqref{pezzo1} and \eqref{pezzo2} in \eqref{ProvaBordoTH} we obtain 
	\left(\mathcal{L}_{1}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\sum_{i=1}^{N}\alpha_{i}}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}
	\left(\widetilde{\mathcal{L}}_{y}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})
